### 2024-10-30 manuscript.tex
Add more co-authors

\documentclass[12pt,a4paper]{article}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage[margin=2cm]{geometry}
\usepackage[citecolor=black]{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{doi}
\usepackage{titlesec}
\usepackage{caption}
\DeclareCaptionLabelSeparator{pipe}{ | }
\captionsetup{labelfont={bf,sf},labelsep=pipe}
\usepackage{graphicx}
\usepackage{lineno}
\linenumbers
\setsansfont{Source Sans Pro}
\setmainfont{EB Garamond}
\setmonofont[Scale=0.8]{SpaceMono}[
	Path=./fonts/,
	Extension=.ttf,
	UprightFont=*-Regular,
	BoldFont=*-Bold,
	ItalicFont=*-Italic,
	BoldItalicFont=*-BoldItalic
]
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald, …}
}
\bibliographystyle{abbrvnat}
\titleformat*{\section}{\large\bfseries\sffamily}
\titleformat*{\subsection}{\normalsize\bfseries\sffamily}
\titlespacing*{\section}{0pt}{14pt}{6pt}
\titlespacing*{\subsection}{0pt}{13pt}{4pt}
\parskip=6pt
\parindent=0pt

@@

\begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$, \ldots\\[0.4cm]
\small
$^\mathsf{1}$Department of Meteorology (MISU) and the Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\
$^\mathsf{2}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\[0.2cm]
*Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
\large \today\\[0.4cm]

@@

PK and FB received funding from the European Union’s Horizon 2020 research and
innovation program under a grant agreement no. 101003470. Supercomputing
resources were provided by the DKRZ (project 1125 ICON-development) and the
National Academic Infrastructure for Supercomputing in Sweden (allocation
2023/22-202). We acknowledge the contribution of Thorsten Mauritsen to funding
acquisition and project management.  We acknowledge the RV \emph{Polarstern}
datasets provided by the Alfred Wegener Institute and Pangaea, the AA15-16
dataset provided by the Australian Antarctic Division (AAD) and University of
Canterbury (UC), RV \emph{Tangaroa} datasets provided by the National Institute
of Water and Atmospheric Research and UC, the NBP1704 dataset provided by the
National Science Foundation, Cooperative Institute for Research in
Environmental Sciences, University of Colorado and UC, the HMNZSW16 dataset
provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by
the Atmospheric Radiation Measurement (ARM) and AAD, and the MICRE dataset
provided by ARM, the Australian Bureau of Meteorology, and AAD. We thank the
scientific staff, the crew, and everyone involved in collecting data on the
voyages and stations, especially Kelly Schick, Peter Guest, John J.  Cassano,
Simon Parsons, Graeme Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.
Harvey (†), Simon P.  Alexander, and Alex Schuddeboom. We acknowledge the ICON
model output provided by the nextGEMS project and the DKRZ, reanalysis dataset
ERA5 provided by the Copernicus Climate Change Service and MERRA-2 provided by
the Global Modeling and Assimilation Office.  Last but not least, we
acknowledge the use of open source software Python, Cython \citep{behnel2011},
TensorFlow \citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011},
NumPy \citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib
\citep{hunter2007}, cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU
Fortran, HDF \citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this
study to the memory of Mike J.  Harvey, who very substantially contributed to
obtaining the atmospheric observations on the RV \emph{Tangaroa} voyages used
in this study.

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage[margin=2cm]{geometry}
\usepackage[citecolor=black]{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{doi}
\usepackage{titlesec}
\usepackage{caption}
\DeclareCaptionLabelSeparator{pipe}{ | }
\captionsetup{labelfont={bf,sf},labelsep=pipe}
\usepackage{graphicx}
\usepackage{lineno}
\linenumbers
\setsansfont{Source Sans Pro}
\setmainfont{EB Garamond}
\setmonofont[Scale=0.8]{SpaceMono}[
	Path=./fonts/,
	Extension=.ttf,
	UprightFont=*-Regular,
	BoldFont=*-Bold,
	ItalicFont=*-Italic,
	BoldItalicFont=*-BoldItalic
]
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald, Graeme Plank, Sean Hartery, Simon Parsons, Simon P. Alexander, Alex J. Schuddeboom, …}
}
\bibliographystyle{abbrvnat}
\titleformat*{\section}{\large\bfseries\sffamily}
\titleformat*{\subsection}{\normalsize\bfseries\sffamily}
\titlespacing*{\section}{0pt}{14pt}{6pt}
\titlespacing*{\subsection}{0pt}{13pt}{4pt}
\parskip=6pt
\parindent=0pt

@@

\begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$, Graeme Plank$^\mathsf{2}$, Sean Hartery$^\mathsf{3}$, Simon Parsons$^\mathsf{4}$, Simon P. Alexander$^\mathsf{5}$, Alex J. Schuddeboom$^\mathsf{2}$, \ldots\\[0.4cm]
\small
$^\mathsf{1}$Department of Meteorology (MISU) and Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\
$^\mathsf{2}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\
$^\mathsf{3}$Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada\\
$^\mathsf{4}$New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia\\
$^\mathsf{5}$Australian Antarctic Division, Kingston, Tasmania, Australia; Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia\\[0.2cm]
*Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
\large \today\\[0.4cm]

@@

PK and FB received funding from the European Union’s Horizon 2020 research and
innovation program under a grant agreement no. 101003470. Supercomputing
resources were provided by the DKRZ (project 1125 ICON-development) and the
National Academic Infrastructure for Supercomputing in Sweden (allocation
2023/22-202). We acknowledge the contribution of Thorsten Mauritsen to funding
acquisition and project management.  We acknowledge the RV \emph{Polarstern}
datasets provided by the Alfred Wegener Institute and Pangaea, the AA15-16
dataset provided by the Australian Antarctic Division (AAD) and University of
Canterbury (UC), RV \emph{Tangaroa} datasets provided by the National Institute
of Water and Atmospheric Research and UC, the NBP1704 dataset provided by the
National Science Foundation, Cooperative Institute for Research in
Environmental Sciences, University of Colorado and UC, the HMNZSW16 dataset
provided by the Royal New Zealand Navy and UC, the MARCUS dataset provided by
the Atmospheric Radiation Measurement (ARM) and AAD, and the MICRE dataset
provided by ARM, the Australian Bureau of Meteorology, and AAD. We thank the
scientific staff, the crew, and everyone involved in collecting data on the
voyages and stations, especially Kelly Schick, Peter Guest, John J.  Cassano,
Sally Garrett, Jamie Halla, and Mike J.  Harvey (†). We acknowledge the ICON
model output provided by the nextGEMS project and the DKRZ, reanalysis dataset
ERA5 provided by the Copernicus Climate Change Service and MERRA-2 provided by
the Global Modeling and Assimilation Office.  Last but not least, we
acknowledge the use of open source software Python, Cython \citep{behnel2011},
TensorFlow \citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011},
NumPy \citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib
\citep{hunter2007}, cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU
Fortran, HDF \citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this
study to the memory of Mike J.  Harvey, who very substantially contributed to
obtaining the atmospheric observations on the RV \emph{Tangaroa} voyages used
in this study.
